The Name of the Title is Hope

### 2020-04-11 paper/paper.tex
update Overview with Ivy

\subsection{Specification Methodology }

>>>>

\subsection{Specification Methodology }
In this section, we present the specification methodology using examples. To specify the S1AP control-plane messaging protocol between the Base-Station(BS) and the MME, we shall use an abstract machine that monitors the protcol events. Conceptually, this machine observes the sequences of message interactions between the two communicating entities( tester and target) by observing the protocol-events triggered by the messages on the wire at the interface between the tester and the network. 
\textcolor{red}{The network is not explicitly modelled in this approach, though there's an assumption that the network may delay or drop or re-order messages, but it shall not create new messages. }
When an event occurs, the abstract machine (which isn't finite state by design) consults its state-representation to determine whether the event conforms to the protocol specification. If so, it updates its state to account for the event, else, \textcolor{red}{it may either marks the occurrence of an illegal event, or ignore it.}

The protocol specification and the monitor are encoded in a language called Ivy. In Ivy, the events associated with messge-packets are modelled by an \textit{action}. Constraints may be imposed upon the state and the parameters upon an event, by defining  some conditions to be satisfied as a pre-condition or a post-condition. If these constraints are satisfied, the event is legal according to the protocol. Else, the events may be considered to be in violation of the protocol.

The protocol state is represented by a collection of functions or relations. The choice between the functional-representation or the relatonial-representation is based on how the state-information shall be queried in downstream actions. The two forms of representation are conceptually equivalent. Any element of the relational-set represents a predicate-abstraction of the actual event.

The properties of the protocol can thus be verified by the communication of abstracted messages between the entities, or it may be used to generate actual messages on the wire, using a \textit{shim} that generates actual network-protocol encoded messages to be sent on the wire, while also capturing the packet events received by the entitiy by tracing packets on the wire. While doing so, the shim triggers the specific protocol-events that get recorded as state-updates within the monitor. It is important to note that the specification is an executable monitor that observes the behaviour of all protocol nodes, in contrast to being an abstract implementation of the protocol entities.

An important capability provided by the Ivy tool, is the capacity to obtain a \textit{generator} that produces random sequences of events that conform to the specification. The generator uses an SMT solver to randomly select a valuation of parameters that satisfy the 'require' constraints enconded in the pre-condition of the selected action. Consequently, the generator helps to generate a random sequence of packet-events in compliance with the protocol-specification that is sent to the test-target.

The S1AP application protocol messages are communicated between the eNodeB and the MME, based on a lower-layer transport protocol based in SCTP( in comparison to UDP or TCP for general data packets over the internet ). We create a shim that connects the abstract packet events to actual SCTP packets on the wire. The \textit{send} and \textit{receive} events are encoded within the shim. The shim is thus an ad-hoc mechanism that connects abstract protocol events of the specification to real-events in the system. Thus, if the socket or other implementation details of the system gets modified, the shim alone may be modified, without altering the protocol specification. This shim, thus helps us to connect the abstract protocol specification, to the physical resources such as the operating system, the networks and compilers to test real-world implementations. \textcolor{red}{It may also be modified to conduct experiments in a simulated environment based on NS3, or be used alone to conduct a formal analysis of the protocol in an abstract theoretically-sound manner. }

The specification may be encoded at a global level, accounting for all the roles that different protocol-entities may play, or at a role-based level, where only the specifications for a single-role are encoded. In the latter case, one needs to effectively assume that the role-being-modelled generates events that are correct according to the protocol, since it's the task of the generator to create the corresponding messages. The task of the verification process is to "guarantee" the correctness of events generated by counterparts of the tester i.e roles played by the be multiple(or single) test targets as required by the protocol design. This framework of Assume/Guarantee specification based testing has an inpmortant formal property: if the composition of roles ever violates the specification, then tehre must exist a failing assume/guarantee test for one of the many roles within the protocol.

\subsection{Specification Examples}
This section shall be updated after we've had some progress in using the tool to model the messsages.
